Anxiety: a decision-theoretic perspective

### 2019-01-31 manuscript/manuscript.tex
section 6

>>>>

In this final section, we want to discuss the relationship between anxiety and
depression. Anxiety and depression are highly comorbid, with roughly 45% of individuals
with lifetime depression diagnosis also diagnosed with at least one anxiety disorder
\citep{kessler2015}. This fact has long been recognized in the clinical literature,
and prominent theories of depression have suggested that anxious control is a necessary
precursor to at least some types of depression \citep{alloy1990}. Recent large-scale
epidemiological studies have provided  some empirical support for this claim, finding that
anxiety symptoms precede and predict the onset of depression \citep{mathew2011, jacobson2014,
kessler2015} (though also see \cite{jacobson2017, plana2019}).

An emerging idea in this literature is that pathological avoidance as a result
of anxiety mediates the transition to depression, perhaps by reduce the likelihood
of experiencing positive events and activities \citep{moitra2008, jacobson2014}.
This finding is perfectly in line with the model presented so far. A sketch of
how this is possible is shown in Figure 6. Under unperturbed learning, avoidable
threat does not impede behavior. Under pessimistic learning, threat can block
future reward. This avoidance can manifest as a failure of behavioral initiation,
or a lack of overall mobility (here represented by an agent self-transitioning
at the starting state). Thus, the model can accomodate the deficits in positive
affect observed in depression as a function of behavioral avoidance, as predicted
by these epidemiological studies.

\begin{figure}
  \centerline{%
    \resizebox{1.0\textwidth}{!}{\includegraphics[trim={0 0 0 0},clip]{../figures/06_lh.png}}%
  }
  \caption{\textbf{Free Choice Premium}}
  \par remember to add parameters
\end{figure}
